Surrogate Regret Bounds for Polyhedral Losses

### 2021-05-28 rates-neurips-21/rates.tex
huber

We observe that Assumption \ref{assumption:lower} captures a wide range of surrogate losses beyond those that are strongly convex and strongly smooth.
For example, exponential loss is not strongly convex, but does satisfy Assumption \ref{assumption:lower}. \bo{more to say?}

>>>>

We observe that Assumption \ref{assumption:lower} captures a wide range of surrogate losses beyond those that are strongly convex and strongly smooth.
For example, exponential loss is not strongly convex, but does satisfy Assumption \ref{assumption:lower}. \bo{more to say?}
Another example is Huber loss\bo{cite?}, which is strongly convex when the prediction is ``close'' to the observation in some sense and linear when ``far''.
For classification with $\Y = \{\pm 1\}$ and prediction space $\reals$, Huber loss can be defined by letting the hinge loss be $t = \max\{0, 1-ry\}$ and setting $L(r)_y = t^2$ if $t \leq 2$, else $4(t-1)$.
